A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-10 article/02_Materials_and_Methods.Rmd
added preliminary simulation figure to text
some work on figure captions

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_graves.jpeg}
\caption{\label{map_graves}This is a figure.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_regions.jpeg}
\caption{\label{map_regions}This is a figure.}
\end{figure}

@@

```{r dprcrosstab, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/dprcrosstab.RData")
dprcrosstab %>% 
  unclass() %>% data.frame() %>% 
  knitr::kable(
    caption = "Table of burial rite distribution within the active dataset",
    format = "latex",
    booktabs = T,
    escape = F,
    linesep = "\\addlinespace"
  ) %>%
  kableExtra::kable_styling(
    full_width = T, 
    font_size = 8,
    latex_options = "hold_position"
  )
```

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_type.jpeg}
\caption{\label{development_burial_type}This is a figure.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_construction.jpeg}
\caption{\label{development_burial_construction}This is a figure.}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/sed_region_matrix.jpeg}
\caption{\label{sed_region_matrix}This is a figure.}
\end{figure*}

@@

```{r distanceandcorrelationtable, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
distance_and_correlation_table %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Mean|Correlation")),
    dplyr::funs(kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black"))) 
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    dplyr::funs(kableExtra::cell_spec(., "latex", bold = . < 0.1)) 
  ) %>%
knitr::kable(
  "latex", 
  caption = "Mean cultural distance, correlation and mantel test results", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type" = 3, "burial construction" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position")
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```

@@

For the actual simulation runs, the parameters were chosen as follows: **TODO**

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_graves.jpeg}
\caption{\label{map_graves}All graves dating between 2200 and 800calBC as extracted from the Radon-B database. The red frame indicates the research area.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_regions.jpeg}
\caption{\label{map_regions}Circular, artificial regions (\textbf{A}) and spatial distance network with classified distance values (\textbf{B}).}
\end{figure}

@@

```{r dprcrosstab, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/dprcrosstab.RData")
dprcrosstab %>% 
  unclass() %>% data.frame() %>% 
  knitr::kable(
    caption = "Burial rite distribution in the active dataset.",
    format = "latex",
    booktabs = T,
    escape = F,
    linesep = "\\addlinespace \\hline \\addlinespace"
  ) %>%
  kableExtra::kable_styling(
    full_width = T, 
    font_size = 9,
    latex_options = "hold_position"
  )
```

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_type.jpeg}
\caption{\label{development_burial_type}Regional distribution time series of the variable \textit{burial type} with the absolute amount (\textbf{A}) and proportion (\textbf{B}) of grave types.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_construction.jpeg}
\caption{\label{development_burial_construction}Like Figure \ref{development_burial_type}, but for the variable \textit{burial construction}.}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/sed_region_matrix.jpeg}
\caption{\label{sed_region_matrix}Plot matrix of the region-region squared euclidian distance time series. In the top right half for the variable \textit{burial type} and in the bottom left for the variable \textit{burial construction}.}
\end{figure*}

@@

```{r distanceandcorrelationtable, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
distance_and_correlation_table %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Mean|Correlation")),
    dplyr::funs(kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black"))) 
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    dplyr::funs(kableExtra::cell_spec(., "latex", bold = . < 0.1)) 
  ) %>%
knitr::kable(
  "latex", 
  caption = "Mean distance, correlation and mantel test results for cultural and spatial distance.", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type" = 3, "burial construction" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position"),
    font_size = 9,
    full_width = T
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```

@@

For the actual simulation runs, the parameters were chosen as follows: **TODO** Figure \ref{simulation*}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/simulation.jpeg}
\caption{\label{simulation}Simulation results in comparison with observed data.}
\end{figure*}
